---
title: "Problem Set 1"
author: "Elmer Camargo + Nick Trella"
subtitle: MGSC 310, Fall 2019, Professor Hersh
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
library(knitr)
# change to your own working directory

knitr::opts_knit$set(root.dir = 'C:/Users/Elmer/Documents/R/Statistical Modeling/PSET1/imdb_dataset')

setwd('C:/Users/Elmer/Documents/R/Statistical Modeling/PSET1/imdb_dataset')

# set seed to your own favorite number
set.seed(1818)
options(width=70)

# general rchunk code options
knitr::opts_chunk$set(
	fig.align = "center",
	fig.height = 4,
	fig.width = 5,
	message = FALSE,
	warning = FALSE,
	autodep = TRUE,
	cache = TRUE,
	cache.comments = FALSE,
	collapse = TRUE,
	size = "vsmall",
	tidy = TRUE,
	tidy.opts = list(width.wrap = 50)
)
opts_chunk$set(message = FALSE,
               warning = FALSE,
               cache = TRUE,
               autodep = TRUE,
               cache.comments = FALSE,
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')


```

## Libraries Needed
```{r}
library("tidyverse")
library("ggplot2") 
library("ggthemes")
library('ggridges')
```

## Question 1: Getting and Setting Working Directories)

```{r}
getwd()
setwd("C:/Users/Elmer/Documents/R/Statistical Modeling/PSET1/imdb_dataset")
```

## Question 2: Reading CSV File)


```{r}
imdb = read.csv("movie_metadata.csv")
```

## Question 3: Dimensions

```{r}
dim(imdb)
```

## Question 4: Variable/Column Names

```{r}
names(imdb)
```

## Question 5: Using ggplot()

```{r Scatter1, fig.width=6, fig.height=4}
sp1 <- 
  ggplot(data = imdb)+ 
  geom_point( mapping = aes(x = imdb_score, y = budget)) +
  labs(x = "IMDB Score",
       y = "Budget",
       title = "IMDB Score by Budget (Categorized by Rating)")+
  ggthemes::theme_economist()

sp1
```

## Question 6: Validating Data and Filtering

```{r}
imdb <- imdb %>% filter(budget < 400000000)
dim(imdb)
```

## Question 7: Using stat_smooth()

```{r Scatter2, fig.width= 6, fig.height= 4}
sp2 <- 
  ggplot(data = imdb)+ 
  geom_point( mapping = aes(x = imdb_score, y = budget)) +
  stat_smooth( mapping = aes(x = imdb_score,y = budget) )+
  labs(x = "IMDB Score",
       y = "Budget",
       title = "IMDB Score by Budget (Categorized by Rating)")+
  ggthemes::theme_economist()

sp2
```

## Question 8: Using facet_wrap()

```{r Scatter3, fig.width=10, fig.height=8}
sp3 <- 
  ggplot(data = imdb)+ 
  geom_point( mapping = aes(x = imdb_score, y = budget)) +
  stat_smooth( mapping = aes(x = imdb_score,y = budget) )+
  facet_wrap(~ content_rating, scales = "free") +
  labs(x = "IMDB Score",
       y = "Budget",
       title = "IMDB Score by Budget (Categorized by Rating)")+
  ggthemes::theme_economist()
sp3
```

## Question 9: Using ggridges

```{r scatter4, echo=FALSE, fig.height=10, fig.width=10}
imdb <- imdb %>% 
  mutate(genre_main = unlist(map(strsplit(as.character(imdb$genres),"\\|"),1)),
         grossM = gross / 1000000,
         budgetM = budget / 1000000)

sp4 <- ggplot(imdb, aes(x = grossM, y = genre_main, fill = genre_main)) + 
  geom_density_ridges() + 
  scale_x_continuous(limits = c(0, 500)) +
  labs(x = "Box Office Gross (USD Millions)", 
       y = "Main Genre",
       title = "Gross by Genre")
sp4
```

## Question 10 Exploring Data

We chose to compare budget and gross across rate PG -13 and R rated movies. Big Budget PG -13 Movies are made for more of a mass appeal in mind (e.g. Fast and Furious, Transformers) with the hopes of major grossing while movies rated R have a much wider range for budgets and grossing. Some rated R movies such The Shape of Water will have a relatively lower budget but still get a high gross because of the critical acclaim. They tend to be more specialized movies where budget isn't as important of a factor in the success of the movie

```{r scatter5, fig.width=10, fig.height=6}
filterd <- imdb %>% filter(content_rating %in% c("PG","R"))

sp5 <- 
  ggplot(data = filterd)+ 
  geom_point( mapping = aes(x = budgetM, y = grossM)) +
  stat_smooth( mapping = aes(x = budgetM,y = grossM) )+
  facet_wrap(~ content_rating, scales = "free") +
  labs(x = "Budget",
       y = "Gross",
       title = "Budget by Gross (Categorized by Rating)")

sp5

```


